Testing gene methylation enrichment analysis approaches using simulated data - summarise data

### 2024-01-01 figs/GSE158422_simulate_summary.Rmd
fig1

@@

@@

>>>>

pdf("fig1a.pdf",width=5,height=4)
barplot(t(x1),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="20 genes per set")
grid()
legend("topleft", inset=.1, c("Precision","Recall","F1"), fill=cols, cex=0.7)
dev.off()

@@

pdf("fig1b.pdf",width=5,height=4)
barplot(t(x2),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="50 genes per set")
grid()
dev.off()

@@

pdf("fig1c.pdf",width=5,height=4)
barplot(t(x3),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="100 genes per set")
grid()
legend("topleft", inset=.1, c("Precision","Recall","F1"), fill=cols, cex=0.7)
dev.off()
